---
title: "Relationship Between Yield of Processing Sweet Corn and Nitrogen (N) Rate"
author: "Maxwel Coura Oliveira, PhD"
institute: "McGill University"
format:
  html:
    theme: journal
editor: visual
execute:
  echo: false
  message: false
  warning: false
---

```{r}
library(kableExtra)
library(tidyverse)
library(reactable)
library(reactablefmtr)
```

**Project requested by** Yves Duquet of [Aliments Nortera (Bonduelle Canada inc)](https://www.bonduelle.com/en/)

## Objective

The primary purpose of the trial is to compare the effect of applied N rates per hectare on the yield and grain quality of two processing sweet corn, [Sh2]{style="background-color:tomato;"} and [Su]{style="background-color:gold;"}. Yields per hectare have become an element of competitiveness between Nortera's production regions, and also against our North American competitors.

## Methods

### Plant material

```{r}
tribble(
  ~Type, ~Description, 
  "Local", "Emile A. Lods Agronomy Research Centre", 
  "Sweet corn", "Su and Sh2", 
  "N", "6 rates", 
  "Seed rate",           "22000 seeds/acre",             
  "Row width",  "75 cm", 
  "Planting time", "June",
  "Plot size", "Width: four rows (3m), Length: 7m",
  "Layout", "Split-plot design"
) |> reactable(theme = fivethirtyeight())
```

### Treatment labels

```{r}
tribble(
  ~Type, ~Treatment, ~`Block 1`, ~`Block 2`, ~`Block 3`, ~`Block 4`,
  "Sh2", "0 kg/ha", "101", "206", "304", "402", 
  "Sh2", "40 kg/ha", "102", "202", "302", "403",          
  "Sh2", "80 kg/ha", "103", "204", "305", "401", 
  "Sh2", "120 kg/ha", "104", "203", "306", "404", 
  "Sh2", "160 kg/ha", "105", "201", "303", "406", 
  "Sh2", "200 kg/ha", "106", "205", "301", "405", 
  "Su", "0 kg/ha", "107", "209", "310", "412", 
  "Su", "40 kg/ha", "108", "210", "309", "408",          
  "Su", "80 kg/ha", "109", "212", "311", "407", 
  "Su", "120 kg/ha", "110", "211", "308", "411", 
  "Su", "160 kg/ha", "111", "207", "312", "409", 
  "Su", "200 kg/ha", "112", "208", "307", "410", 
) -> trt

trt_col <- trt %>% 
  mutate(col = dplyr::case_when(
  Type == "Sh2" ~ 'tomato',
  TRUE ~ 'gold'
  ))

trt |> 
  reactable(pagination = FALSE,
            theme = fivethirtyeight(),
            defaultSorted = 'Type',
  defaultColDef = colDef(
    style = color_scales(trt_col, color_ref = 'col')),
  columns = list(car_colors = colDef(show = FALSE))
)
```

```{r}

```

### Trial map

#### Option 1

**Long width / Short length:** 12 plots in each block.

**Size:** 36 m (width) x 28 m (length)[^1]

[^1]: It might be needed to add extra space in between blocks for the planter turning around plots

**Treatments:** Number ending in 1 to 6 are [Sh2]{style="background-color:tomato;"} and treatments ending in 7 to 12 are [Su]{style="background-color:gold;"}.

```{r}
tribble(
  ~Block, ~`1`, ~`2`, ~`3`, ~`4`, ~`5`, ~`6`, ~`7`, ~`8`, ~`9`, ~`10`, ~`11`, ~`12`,
  "Block 4", "407", "408", "409", "410", "411", "412", "401", "402", "403", "404", "405", "406", 
  "Block 3", "301", "302", "303", "304", "305", "306", "307", "308", "309", "310", "311", "312",
  "Block 2", "207", "208", "209", "210", "211", "212", "201", "202", "203", "204", "205", "206", 
  "Block 1", "101", "102", "103", "104", "105", "106", "107", "108", "109", "110", "111", "112"
) |> 
  mutate(Block = as_factor(Block)) |> 
  mutate_if(is_character, as.double) -> opt1
```

```{r}
opt_col <- opt1 %>% 
  mutate(colors = dplyr::case_when(
  `1` == 101 | `1` == 301  ~ 'tomato',
  `2` == 102 & `2` == 302  ~ 'tomato',
  `3` == 103 & `3` == 303  ~ 'tomato',
  `4` == 104 & `4` == 304  ~ 'tomato',
  `5` == 105 & `5` == 305  ~ 'tomato',
  `6` == 106 & `6` == 306  ~ 'tomato',
  TRUE ~ 'gold'
  ))  |> 
  mutate(colors2 = dplyr::case_when(
  `7` == 107 | `1` == 307  ~ 'gold',
  `8` == 108 | `8` == 308  ~ 'gold',
  `9` == 109 & `9` == 309  ~ 'gold',
  `10` == 110 & `10` == 310  ~ 'gold',
  `11` == 111 & `11` == 311  ~ 'gold',
  `12` == 112 & `11` == 312  ~ 'gold',
  TRUE ~ 'tomato'
  ))
```

```{r}
opt1 |> 
   reactable(pagination = FALSE,
               theme = fivethirtyeight(),
  columns = list(
    Block = colDef(name = ""),
    `1` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors')),
    `2` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors')),
    `3` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors')),
    `4` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors')),
    `5` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors')),
    `6` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors')),
    `7` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors2')),
    `8` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors2')),
    `9` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors2')),
    `10` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors2')),
    `11` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors2')),
    `12` = colDef(name = "", style = color_scales(opt_col, color_ref = 'colors2'))
    ))
```

#### Option 2

**Short width / Long length:** 6 plots in each block, 6 other plots on top.

**Size:** 18 m (width) x 56 m (length)[^2]

[^2]: It might be needed to add extra space in between blocks for the planter turning around plots

**Treatments:** Number ending in 1 to 6 are [Sh2]{style="background-color:tomato;"} and treatments ending in 7 to 12 are [Su]{style="background-color:gold;"}.

```{r}
tribble(
  ~Block, ~`1`, ~`2`, ~`3`, ~`4`, ~`5`, ~`6`, 
  "Block 4", "407", "408", "409", "410", "411", "412",
  "", "401", "402", "403", "404", "405", "406", 
  "Block 3", "307", "308", "309", "310", "311", "312",
  "", "301", "302", "303", "304", "305", "306", 
  "Block 2", "207", "208", "209", "210", "211", "212",
  "", "201", "202", "203", "204", "205", "206", 
  "Block 1", "107", "108", "109", "110", "111", "112",
  "", "101", "102", "103", "104", "105", "106"
) -> opt2
```

```{r}
opt_col2 <- opt2 %>% 
  mutate(colors = dplyr::case_when(
  `1` == 101 | `1` == 201 | `1` == 301 | `1` == 401 ~ 'tomato',
  `2` == 102 | `2` == 202 | `2` == 302 | `2` == 402 ~ 'tomato',
  `3` == 103 | `3` == 203 | `3` == 303 | `3` == 403 ~ 'tomato',
  `4` == 104 | `4` == 204 | `4` == 304 | `4` == 404 ~ 'tomato',
  `5` == 105 | `4` == 205 | `4` == 305 | `4` == 405 ~ 'tomato',
  `6` == 106 | `4` == 206 | `4` == 306 | `4` == 406 ~ 'tomato',
  TRUE ~ 'gold'
  )) 
```

```{r}
opt2 |> 
  reactable(pagination = FALSE,
               theme = fivethirtyeight(),
  columns = list(
    Block = colDef(name = ""),
    `1` = colDef(name = "", style = color_scales(opt_col2, color_ref = 'colors')),
    `2` = colDef(name = "", style = color_scales(opt_col2, color_ref = 'colors')),
    `3` = colDef(name = "", style = color_scales(opt_col2, color_ref = 'colors')),
    `4` = colDef(name = "", style = color_scales(opt_col2, color_ref = 'colors')),
    `5` = colDef(name = "", style = color_scales(opt_col2, color_ref = 'colors')),
    `6` = colDef(name = "", style = color_scales(opt_col2, color_ref = 'colors'))
    ))
```

```{r}
#| include: false

tribble(
  ~Su_1, ~Sh2_1, ~Su_2, ~Sh2_2, ~Su_3, ~Sh2_3, ~Su_4, ~Sh2_4,
  "101", "107", "201", "207", "301", "307", "401", "407",
  "102", "108", "202", "208", "302", "308", "402", "408",
  "103", "109", "203", "209", "303", "309", "403", "409",
  "104", "110", "204", "210", "304", "310", "404", "410",
  "105", "111", "205", "211", "305 ", "311", "405", "411",
  "106", "112", "206", "212", "306", "312", "406", "412"
) -> trial
#  mutate_if(is_character, as.double) 
trial |> 
  reactable(
    theme = fivethirtyeight(),
    columns = list(
    Su_1 = colDef(name = "Su", align = "center"),
    Sh2_1 = colDef(name = "Sh2", align = "center"),
    Su_2 = colDef(name = "Su", align = "center"),
    Sh2_2 = colDef(name = "Sh2", align = "center"),
    Su_3 = colDef(name = "Su", align = "center"),
    Sh2_3 = colDef(name = "Sh2", align = "center"),
    Su_4 = colDef(name = "Su", align = "center"),
    Sh2_4 = colDef(name = "Sh2", align = "center")
  ),
    columnGroups = list(
    colGroup(name = "Block 1", columns = c("Su_1", "Sh2_1"), align = "center"), 
    colGroup(name = "Block 2", columns = c("Su_2", "Sh2_2"), align = "center"),
    colGroup(name = "Block 3", columns = c("Su_3", "Sh2_3"), align = "center"),
    colGroup(name = "Block 4", columns = c("Su_4", "Sh2_4"), align = "center")
    )
  )
```

## Inputs

```{r}
tribble(
  ~Input, ~Product, ~Rate, ~Type, ~Timing,
  "Fertilizer", "28.9-9.6-14.4", "325 kg/ha",  "Broadcast",    "Pre-seeding",
  "",           "N",             "6 N treatments", "Side-dressed", "Height of 15-20 cm",
  "Herbicide",  "Primextra II Magnum", "4 L/ha", "Pre-emergence", "Up to 3 days after planting"
) |> reactable(theme = fivethirtyeight())
```
